Recent demography drives changes in linked selection across the maize genome

### 2015-11-25 NatGen/manuscript.tex
natgen
abstract

% fancy for Nature Genetics
\fancyhead[RO]{\begin{picture}(600,1)(10,20)\put(440,32) {\textcolor{Dgreen}{\large{\sfbf{ARTICLES}}}}\end{picture}}
\fancyhead[RE]{\begin{picture}(600,1)(10,20)\put(10,32)  {\textcolor{Dgreen}{\large{\sfbf{ARTICLES}}}}\end{picture}}
\fancyhead[C]{\begin{picture}(600,1)(10,20)\linethickness{50pt}\put(-43,52) {{\color{pTop}{\line(1,0){615}}}}\linethickness{0.5pt}\put(10,-678) {{\line(1,0){515}}}\end{picture}}

@@

\begin{abstract}
  \noindent \bf
  \noindent
Across species, genetic diversity is shaped by the interaction of drift and selection. But the details of this interaction are not well understood. Although a population's propensity to drift is typically summarized by its long-term effective population size ($N_e$ ), rapidly changing population demographics complicate this relationship. To better understand how changing demography impacts selection, we used whole-genome sequencing data to investigate patterns of linked selection in domesticated and wild maize (teosinte). We produce the first unconfounded estimate of $N_e$ at the onset of maize domestication, which shows that maize was reduced to approximately 5\% the population size of teosinte before it experienced rapid expansion post-domestication. As expected, a reduced population size during domestication decreased the efficiency selection, but rapid expansion after domestication has since increased the efficiency of selection to levels exceeding those seen in teosinte. This final observation is applicable to all species that have undergone recent demographic change, including humans, domesticates, model, and non-model species. It demonstrates that rapid demographic change can have immediate and wide-ranging impacts on diversity that conflict with would-be expectations based on $N_e$ alone.
\end{abstract}

@@

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
\bibliographystyle{naturemag}
\bibliography{Reference}
}

>>>>

% fancy for Nature Genetics
\fancyhead[RO]{\begin{picture}(600,1)(10,20)\put(440,32) {\textcolor{Dgreen}{\large{\sfbf{ANALYSIS}}}}\end{picture}}
\fancyhead[RE]{\begin{picture}(600,1)(10,20)\put(10,32)  {\textcolor{Dgreen}{\large{\sfbf{ANALYSIS}}}}\end{picture}}
\fancyhead[C]{\begin{picture}(600,1)(10,20)\linethickness{50pt}\put(-43,52) {{\color{pTop}{\line(1,0){615}}}}\linethickness{0.5pt}\put(10,-678) {{\line(1,0){515}}}\end{picture}}

@@

\begin{abstract}
  \noindent \bf
  \noindent
Genetic diversity is shaped by the interaction of drift and selection, but the details of this interaction are not well understood. Although a population's propensity to drift is typically summarized by its long-term effective population size ($N_e$ ), rapidly changing population demographics complicate this relationship. To better understand how changing demography impacts selection, we used whole-genome sequencing data to investigate patterns of linked selection in domesticated and wild maize (teosinte). We produce the first whole-genome estimate of the demography of maize domestication, showing that maize was reduced to approximately 5\% the population size of teosinte before it experienced rapid expansion post-domestication to population sizes much larger than its ancestor. Evaluation of patterns of nucleotide diversity in and near genes shows little evidence of selection on beneficial amino acid substitutions, and that the domestication bottleneck lead to a decline in the efficiency of purifying selection in maize.  Young alleles, however, show evidence of much stronger purifying selection in maize, reflecting the much larger effective size of present day populations. Our results demonstrate that recent demographic change --- a hallmark of many species including both humans and crops ----  can have immediate and wide-ranging impacts on diversity that conflict with would-be expectations based on $N_e$ alone.
\end{abstract}

@@

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
\bibliographystyle{naturemag}
%\bibliographystyle{NatureSeriesT}
\bibliography{Reference}
}
